The Ky Fan Norms and Beyond: Dual Norms and Combinations for Matrix Optimization

### 2025-11-26 conf_article/neon.tex
Added loads of pictures for CIFAR

We log train and validation accuracy, and nuclear, gradient, and spectral norms of the gradients of conv1.weight and conv2.weight for all the layers.

@@

>>>>

We log train and validation accuracy, and nuclear, gradient, and spectral norms of the gradients of conv1.weight and conv2.weight for all the layers. The gradient norms decrease only by the order of ten maximum during training, while train accuracy reaches full 100\% for Muon, S-Muon, and F-Muon.

@@

\begin{figure}[h!]
    \centering
    \begin{subfigure}[t]{0.7\linewidth}
        \centering
        \includegraphics[width=\linewidth]{figs/cifar_logger/total_frobenius.pdf}
        \caption{Total Frobenius norm}
		\label{fig:total_fro_norm_cifar}
    \end{subfigure}
    \vspace{1em} % optional: add vertical spacing between subfigures
    \begin{subfigure}[t]{0.7\linewidth}
        \centering
        \includegraphics[width=\linewidth]{figs/cifar_logger/total_spectral.pdf}
        \caption{Total spectral norm}
		\label{fig:total_spectral_norm_cifar}
    \end{subfigure}
	\vspace{1em} % optional: add vertical spacing between subfigures
    \begin{subfigure}[t]{0.7\linewidth}
        \centering
        \includegraphics[width=\linewidth]{figs/cifar_logger/total_nuclear.pdf}
        \caption{Total nuclear norm}
		\label{fig:total_nuclear_norm_cifar}
    \end{subfigure}
    \caption{Matrix norms of the whole gradient of CIFAR CNN}
	\label{fig:total_norms_cifar}
\end{figure}

% Juxtaposed conv1 (left) vs conv2 (right) norms

\begin{figure}[h!]
    \centering
    %--- First row: Frobenius ---
    \begin{subfigure}[t]{0.45\linewidth}
        \centering
        \includegraphics[width=\linewidth]{figs/cifar_logger/layers_2_conv1_weight_frobenius.pdf}
        \caption{Frobenius norm of layer2.conv1}
        \label{fig:fro_conv1}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.45\linewidth}
        \centering
        \includegraphics[width=\linewidth]{figs/cifar_logger/layers_2_conv2_weight_frobenius.pdf}
        \caption{Frobenius norm of layer2.conv2}
        \label{fig:fro_conv2}
    \end{subfigure}

    \vspace{1em}

    %--- Second row: Spectral ---
    \begin{subfigure}[t]{0.45\linewidth}
        \centering
        \includegraphics[width=\linewidth]{figs/cifar_logger/layers_2_conv1_weight_spectral.pdf}
        \caption{Spectral norm of layer2.conv1}
        \label{fig:spec_conv1}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.45\linewidth}
        \centering
        \includegraphics[width=\linewidth]{figs/cifar_logger/layers_2_conv2_weight_spectral.pdf}
        \caption{Spectral norm of layer2.conv2}
        \label{fig:spec_conv2}
    \end{subfigure}

    \vspace{1em}

    %--- Third row: Nuclear ---
    \begin{subfigure}[t]{0.45\linewidth}
        \centering
        \includegraphics[width=\linewidth]{figs/cifar_logger/layers_2_conv1_weight_nuclear.pdf}
        \caption{Nuclear norm of layer2.conv1}
        \label{fig:nuc_conv1}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.45\linewidth}
        \centering
        \includegraphics[width=\linewidth]{figs/cifar_logger/layers_2_conv2_weight_nuclear.pdf}
        \caption{Nuclear norm of layer2.conv2}
        \label{fig:nuc_conv2}
    \end{subfigure}

    \caption{Matrix norms of layer2.conv1 (left) and layer2.conv2 (right) gradients of CIFAR CNN}
    \label{fig:norms_conv1_vs_conv2}
\end{figure}
